### 2018-10-13 tex/abstract.tex
Version 2.0

In large-scale data-parallel analytics, \textit{shuffle}, or the cross-network read and aggregation of partitioned data between tasks with data dependencies, usually brings in large network transfer overhead.
Due to the dependency constrains, execution of those descendant tasks could be delayed by logy shuffles.
To reduce shuffle overhead, we present \textit{SCache}, an open source \footnote{The URL is omitted due to double-blinded review requirements.} plug-in system that particularly focuses on shuffle optimization in frameworks defining jobs as \textit{directed acyclic graphs} (DAGs). 
{\color{blue}
During shuffle optimization process, we propose a performance model called \textit{Framework Resources Quantification}(FRQ) model. 
FRQ model displays utilization of resources in time dimension and calculate exectuion time of computing jobs on different DAG frameworks. 
We use FRQ model to assist in analyzing shuffle process and verify SCache shuffle optimization by mathematics.
}
By extracting and analyzing the DAGs and shuffle dependencies prior to the actual task execution, SCache can take full advantage of the system memory to accelerate the shuffle process. Meanwhile, it adopts heuristic-MinHeap scheduling combining with shuffle size prediction to pre-fetch shuffle data and balance the total size of data that will be processed by each descendant task on each node. 
% {\color{red}
% We have implemented SCache and customized Spark to use it as the external shuffle service and co-scheduler. The performance of SCache is evaluated with both simulations and testbed experiments on a 50-node Amazon EC2 cluster.
% Those evaluations have demonstrated that, by incorporating SCache, the shuffle overhead of Spark can be reduced by nearly $89\%$, and the overall completion time of TPC-DS queries improves $40\%$ on average.
% }
{\color{blue}
We have implemented SCache as the external shuffle service and co-scheduler on both Apache Spark and Apache Hadoop. The performance of SCache is evaluated with both simulations and testbed experiments on a 50-node Amazon EC2 cluster.
Those evaluations have demonstrated that, by incorporating SCache, the shuffle overhead of Spark can be reduced by nearly $89\%$, and the overall completion time of TPC-DS queries improves $40\%$ on average. On Apache Hadoop, Scache optimize end-to-end Terasort completion time by 15\%.
}
\end{abstract}

>>>>

In large-scale data-parallel analytics, shuffle, or the cross-network read and aggregation of partitioned data between tasks with data dependencies, usually brings in large overhead. Due to the dependency constrains, execution of those descendant tasks could be delayed by logy shuffles.
To reduce shuffle overhead, we present \textit{SCache}, an open source plug-in system that particularly focuses on shuffle optimization. 
{\color{blue}
During shuffle optimization process, we propose a performance model called \textit{Framework Resources Quantification}(FRQ) model. 
FRQ model displays utilization of resources in time dimension and calculate exectuion time of computing jobs on different DAG frameworks. 
We use FRQ model to assist in analyzing shuffle process and verify SCache shuffle optimization by mathematics.
}
By extracting and analyzing shuffle dependencies prior to the actual task execution, SCache can adopt heuristic pre-scheduling combining with shuffle size prediction to pre-fetch shuffle data and balance load on each node. 
Meanwhile, SCache takes full advantage of the system memory to accelerate the shuffle process. 
% {\color{red}
% We have implemented SCache and customized Spark to use it as the external shuffle service and co-scheduler. The performance of SCache is evaluated with both simulations and testbed experiments on a 50-node Amazon EC2 cluster.
% Those evaluations have demonstrated that, by incorporating SCache, the shuffle overhead of Spark can be reduced by nearly $89\%$, and the overall completion time of TPC-DS queries improves $40\%$ on average.
% }
{\color{blue}
We have implemented SCache as the external shuffle service and co-scheduler on both Apache Spark and Apache Hadoop. The performance of SCache is evaluated with both simulations and testbed experiments on a 50-node Amazon EC2 cluster.
Those evaluations have demonstrated that, by incorporating SCache, the shuffle overhead of Spark can be reduced by nearly $89\%$, and the overall completion time of TPC-DS queries improves $40\%$ on average. On Apache Hadoop, Scache optimize end-to-end Terasort completion time by 15\%.
}
\end{abstract}

### 2018-10-13 tex/conclusion.tex
Version 2.0

\section{Conclusion}
 In this paper, we present SCache, a cross-framework open source shuffle optimization system for DAG computing frameworks. SCache decouples the shuffle from computing pipeline and leverages shuffle data pre-fetching to mitigate the I/O overhead of the whole system. By scheduling tasks with application context, SCache bridges the gap among computing stages. 
%  {\color{red}
%  Our implementation with Spark and evaluations show that SCache can provide a promising speedup to the DAG framework. 
%  }
 {\color{blue}
 At the expense of inserting hundred lines of code, we adapt Spark and Hadoop Mapreduce to SCache. Our evaluation result shows that SCache can provide a promising speedup to the DAG framework. 
 Furthermore, we propose \textit{Framework Resources Quantification}(FRQ) model to assist in analyzing shuffle process of DAG computing frameworks. At last we use FRQ model to verify SCache shuffle optimization by mathematics.
 Therefore we believe that SCache is a simple and efficient system to enhance the performance of most DAG computing frameworks. 
 }

>>>>

\section{Conclusion}
In this paper, we present SCache, a cross-framework shuffle optimization for DAG computing frameworks. 
SCache decouples the shuffle from computing tasks and leverages memory to store shuffle data. 
By tasks pre-scheduling and shuffle data pre-fetching with application context, SCache significantly mitigates the shuffle overhead. 
%  {\color{red}
%  Our implementation with Spark and evaluations show that SCache can provide a promising speedup to the DAG framework. 
%  }
{\color{blue}
Our evaluations on Spark and Hadoop Mapreduce with SCache show that SCache can provide a promising speedup. 
Furthermore, we propose \textit{Framework Resources Quantification}(FRQ) model to assist in analyzing shuffle process of DAG computing frameworks. At last we use FRQ model to verify SCache shuffle optimization by mathematics.
Therefore, with the shared defects of shuffle among different frameworks, we believe that the optimization of SCache is general and easy to adapt. 
}

### 2018-10-13 tex/evaluation.tex
Version 2.0

\section{Evaluation}\label{evaluation}
This section reveals the evaluation of SCache with comprehensive workloads and benchmarks. 
First we run a simple DAG job with single shuffle to analyze hardware utilization and impact of shuffle optimization from the scope of a task to a job. 
Then we use a recognized shuffle intensive benchmark --- Terasort to evaluate SCache with different data partition schemes.

@@

In order to prove the performance gain of SCache with a real production workload, we also evaluate Spark TPC-DS \footnote{https://github.com/databricks/spark-sql-perf} and present the overall performance improvement.
{\color{blue}
To prove SCache compatibility as a cross-framework plug-in, we implemented SCache on both Hadoop MapReduce and Spark. 
Due to the simple DAG computing in Hadoop MapReduce, we only use Terasort as a shuffle-heavy benchmark to evaluate the performance of Hadoop Mapreduce with SCache.
}
At last, we measure the overhead of weighted reservoir sampling. 
In short, SCache can decrease ~$89\%$ time of Spark shuffle. Furthermore, SCache achieves a ~$75\%$ and ~$50\%$ improvement of reduce stage completion time respectively in simple DAG application and Terasort without introducing extra network traffic. More impressively, the overall completion time of TPC-DS can be improved ~$40\%$ on average by applying optimization from SCache.
{\color{blue}Meanwhile, Hadoop Mapreduce with Scache optimize job completion time by up to 15\% and an average of 13\%}

@@

\subsection{Setup}\label{stepup}
We implement a Spark demon to enable shuffle optimization as a representative.
We run our experiments on a 50 m4.xlarge nodes cluster on Amazon EC2 \footnote{http://aws.amazon.com/ec2/}. Each node has 16GB memory and 4 CPUs. The network bandwidth is not specifically provided by Amazon. Our evaluations reveal the bandwidth is about 300 Mbps (see Figure \ref{fig:util}).

\subsection{Simple DAG Analysis}
%\subsubsection{Hardware Utilization}
We first run the same single shuffle test as mentioned in Figure \ref{fig:util}. As shown in Figure \ref{fig:scache_util}, the hardware utilization is captured from one node during the job. Note that since the completion time of whole job is about $50\%$ less than Spark without SCache, the duration of Figure \ref{fig:scache_util} is cut in half as well. An overlap among CPU, disk, and network can be easily observed in Figure \ref{fig:scache_util}. That is, SCache prevents the computing process from being cutting off by the I/O operations with a fine-grained resource allocation. It ensures the overall CPU utilization of the cluster stays in a high level. In addition, the decoupling of shuffle write helps free the CPU earlier and leads to a faster map task computation. At the same time, the shuffle pre-fetching in the early stage of map phase shifts the network transfer completion time, which decreases reduce stage completion time. The combination is the main performance gain we achieved on the scope of hardware utilization by SCache.
% \begin{figure}
% 	%\vspace*{-0.01cm}
% 	\begin{subfigure}{\linewidth}
% 		\centering
% 		\includegraphics[width=0.6\linewidth]{fig/groupbymapstage}
% 		\caption{Map Stage Completion Time Comparison}
% 		\label{fig:mapstage}
% 	\end{subfigure}
% 	\begin{subfigure}{\linewidth}
% 		\centering
% 		\includegraphics[width=0.6\linewidth]{fig/groupbyreducestage}
% 		\caption{Reduce Stage Completion Time Comparison}
% 		\label{fig:reducestage}
% 	\end{subfigure}
% 	\caption{Stage Completion Time of Single Shuffle Test}
% 	\label{fig:singleshuffle}
% \end{figure}

% \begin{figure}
% 	\begin{subfigure}{\linewidth}
% 		\centering
% 		\includegraphics[width=0.6\linewidth]{fig/groupbymaptask}
% 		\caption{Median Task Details in Map Stages}
% 		\label{fig:maptask}
% 	\end{subfigure}
% 	\begin{subfigure}{\linewidth}
% 		\centering
% 		\includegraphics[width=0.6\linewidth]{fig/groupbyreducetask}
% 		\caption{Median Task Details in Reduce Stages}
% 		\label{fig:reducetask}
% 	\end{subfigure}
% 	\caption{Median Task Completion Time of Single Shuffle Test}
% 	\label{fig:singleshuffletask}
% \end{figure}
The performance evaluation in Figure \ref{fig:singleshuffletask} shows the consistent results with our analysis on hardware utilization. For each stage, we run 5 rounds of tasks with different input size. By running spark with SCache, the completion time of map stage can be reduced $10\%$ on average. For reduce stage, instead, SCache achieves a ~$75\%$ performance gain in the completion time of the reduce stage.

A detail analysis into the nutshell of varied overall performance gain on different stages is presented with Figure \ref{fig:singleshuffletask}. For each stage, we pick the median task. About 40\% of shuffle write time can be eliminated by SCache (Figure \ref{fig:maptask}) in a map task. Because the serialization of data is CPU intensive \cite{makingsense} and it is inevitable while moving data out of JVM, SCache can not eliminate the whole phase of shuffle write. It results in a less performance gain in the map stage.
On the other hand, the network transfer introduces a significantly latency in shuffle read of reduce task (Figure \ref{fig:reducetask}). By doing shuffle data pre-fetching for the reduce tasks, the shuffle read time decreases ~$100\%$. That is, the explicit network transfer is perfectly overlapped by SCache shuffle pre-fetching. In overall, SCache can help Spark decrease by ~$89\%$ time in the whole shuffle process. In addition, heuristic reduce tasks scheduling achieves better load balance in cluster than the Spark default FIFO scheduling which may randomly assign two heavy tasks on a single node. So that we can have a significant performance gain in the completion time of the reduce stage.

\subsection{Terasort}
We also evaluate Terasort --- a recognized shuffle intensive benchmark for distributed system analysis.
Terasort consists of two consecutive shuffles. The first shuffle reads the input data and uses a customized hash partition function for re-partitioning. The second shuffle partitions the data through a range partitioner. As the range bounds set by range partitioner almost match the same pattern of the first shuffle, almost $93\%$ of input data is from one particular map task for each reduce task. So we take the second shuffle as an extreme case to evaluate the scheduling locality for SCache.

As shown in Figure \ref{fig:terasort}, we present the first shuffle as the evaluation of shuffle optimization. At the same time, we use the second shuffle to evaluate in the dimension of scheduling locality (Figure \ref{fig:terashuffle}). For the first shuffle, Spark with SCache runs 2 $\times$ faster during the reduce stage with the input data in a range from 10GB to 200GB. At the same time, Figure \ref{fig:terashuffle} reveals that SCache pre-scheduling produces exactly same network traffic of the second shuffle as Spark, which implies that SCache pre-scheduling can obtain the best locality while balancing the load. In contrast, Spark delays scheduling reduce tasks with the shuffle map output to achieve this optimum.

@@

\subsection{Production Workload}
We also evaluate some shuffle heavy queries from TPC-DS. TPC-DS benchmark is designed for modeling multiple users submitting varied queries (e.g. ad-hoc, interactive OLAP, data mining, etc.). TPC-DS contains 99 queries and is considered as the standardized industry benchmark for testing big data systems. We evaluate the performance of Spark with SCache by picking some of the TPC-DS queries with shuffle intensive attribute. 
As shown in Figure \ref{fig:tpcds}, the horizontal axis is query number, and the vertical axis is query completion time. Spark with SCache outperforms the original Spark in almost all the queries. Furthermore, in many queries, Spark with SCache outperforms original Spark by an order of magnitude. The overall reduction portion of query time that SCache achieved is 40\% on average. Since this evaluation presents the overall job completion time of queries, we believe that our shuffle optimization is promising.
% \begin{figure}
% 	\begin{subfigure}{\linewidth}
% 		\centering
% 		\includegraphics[width=0.6\linewidth]{fig/tera}
% 		\caption{Reduce Stage Completion Time Comparison of First Shuffle}
% 		\label{fig:terasort}
% 	\end{subfigure}
% 	\vspace{0.08cm}
% 	\begin{subfigure}{\linewidth}
% 		\centering
% 		\includegraphics[width=0.6\linewidth]{fig/tera_shuffle}
% 		\caption{Shuffle Data through Network Comparison of Second Shuffle}
% 		\label{fig:terashuffle}
% 	\end{subfigure}
% 	\caption{Terasort Evaluation}
% \end{figure}
\subsection{Overhead of Sampling}
In this part, we evaluate the overhead of sampling with different input data sizes on one node and cluster scales. In Figure \ref{fig:sampling}, the overhead of sampling only grows with the increase of input size on each node. But it remains relatively stable when the cluster size scales up. It makes SCache a scalable system in cluster.

>>>>

\section{Evaluation}\label{evaluation}
This section reveals the evaluation of SCache with comprehensive workloads and benchmarks. 
First we run a job with single shuffle to analyze hardware utilization and see the impacts of different components from the scope of a task to a job. 
Then we use a recognized shuffle intensive benchmark --- Terasort to evaluate SCache with different data partition schemes.

@@

In order to prove the performance gain of SCache with a real production workload, we also evaluate Spark TPC-DS\footnote{https://github.com/databricks/spark-sql-perf} and present the overall performance improvement.
{\color{blue}
To prove SCache compatibility as a cross-framework plug-in, we implemented SCache on both Hadoop MapReduce and Spark. 
Due to the simple DAG computing in Hadoop MapReduce, we only use Terasort as a shuffle-heavy benchmark to evaluate the performance of Hadoop Mapreduce with SCache.
}
Finally, we measure the overhead of weighted reservoir sampling. 
In summary, SCache can decrease ~$89\%$ time of Spark shuffle without introducing extra network transfer.
More impressively, the overall completion time of TPC-DS can be improved ~$40\%$ on average by applying the optimization from SCache.
{\color{blue}Meanwhile, Hadoop Mapreduce with Scache optimize job completion time by up to 15\% and an average of 13\%}

@@

\subsection{Setup}\label{stepup}
We modified Spark to enable shuffle optimization of SCache as a representative.
The shuffle configuration of Spark is set to the default\footnote{http://spark.apache.org/docs/1.6.2/configuration.html}. 
We run the experiments on a 50-node m4.xlarge cluster on Amazon EC2\footnote{http://aws.amazon.com/ec2/}. 
Each node has 16GB memory and 4 CPUs. The network bandwidth provided by Amazon is insufficient. 
Our evaluations reveal the bandwidth is only about 300 Mbps (see Figure \ref{fig:util}).

\subsection{Simple DAG Analysis}
%\subsubsection{Hardware Utilization}
We first run the same single shuffle test shown in Figure \ref{fig:util}. 
For each stage, we run 5 rounds of tasks with different input size. 
As shown in Figure \ref{fig:scache_util}, the hardware utilization is captured from one node during the job. 
Note that since the completion time of whole job is about $50\%$ less than Spark without SCache, the duration of Figure \ref{fig:scache_util} is cut in half as well. 
An overlap among CPU, disk, and network can be easily observed in Figure \ref{fig:scache_util}. 
It is because the decoupling of shuffle prevents the computing resource from being blocked by I/O operations. 
On the one hand, the decoupling of shuffle write helps free the slot earlier, so that it can be re-scheduled to a new map task.
On the other hand, with the help of shuffle pre-fetching, the decoupling of shuffle read significantly decreases the CPU idle time at the beginning of a reduce task.
At the same time, SCache manages the hardware resources to store and transfer shuffle data without interrupting the computing process.
As a result, the utilization and multiplexing of hardware resource are increased, thus improving the performance of Spark. 
% \begin{figure}
% 	%\vspace*{-0.01cm}
% 	\begin{subfigure}{\linewidth}
% 		\centering
% 		\includegraphics[width=0.6\linewidth]{fig/groupbymapstage}
% 		\caption{Map Stage Completion Time Comparison}
% 		\label{fig:mapstage}
% 	\end{subfigure}
% 	\begin{subfigure}{\linewidth}
% 		\centering
% 		\includegraphics[width=0.6\linewidth]{fig/groupbyreducestage}
% 		\caption{Reduce Stage Completion Time Comparison}
% 		\label{fig:reducestage}
% 	\end{subfigure}
% 	\caption{Stage Completion Time of Single Shuffle Test}
% 	\label{fig:singleshuffle}
% \end{figure}

% \begin{figure}
% 	\begin{subfigure}{\linewidth}
% 		\centering
% 		\includegraphics[width=0.6\linewidth]{fig/groupbymaptask}
% 		\caption{Median Task Details in Map Stages}
% 		\label{fig:maptask}
% 	\end{subfigure}
% 	\begin{subfigure}{\linewidth}
% 		\centering
% 		\includegraphics[width=0.6\linewidth]{fig/groupbyreducetask}
% 		\caption{Median Task Details in Reduce Stages}
% 		\label{fig:reducetask}
% 	\end{subfigure}
% 	\caption{Median Task Completion Time of Single Shuffle Test}
% 	\label{fig:singleshuffletask}
% \end{figure}
The performance evaluation in Figure \ref{fig:singleshuffletask} shows the consistent results with our observation of hardware utilization. 
% By running Spark with SCache, the completion time of map stage can be reduced $10\%$ on average. 
% For reduce stage, instead, SCache achieves a ~$75\%$ performance gain in the completion time of the reduce stage.
% A detail analysis into the nutshell of varied overall performance gain on different stages is presented with Figure \ref{fig:singleshuffletask}. 
For each stage, we pick the task that has median completion time. 
In the map task, the disk operations are replaced by the memory copies to decouple the shuffle write. 
It helps eliminate ~40\% of shuffle write time (Figure \ref{fig:maptask}), which leads to a $10\%$ improvement of map stage completion time in Figure \ref{fig:mapstage}. 
Note that the shuffle write time can be observed even with the optimization of SCache. 
The reason is that before moving data out of Spark's JVM, the serialization is inevitable and CPU intensive \cite{makingsense}.

In the reduce task, most of the shuffle overhead is introduced by network transfer delay. 
By doing shuffle data pre-fetching based on the pre-scheduling results, the explicit network transfer is perfectly overlapped in the map stage. 
With the help of the co-scheduling scheme, SCache guarantees that each reduce task has the benefit of shuffle pre-fetching. 
The in-memory cache of shuffle data further reduce the shuffle read time. 
As a result, the combination of these optimizations decreases ~$100\%$ overhead of the shuffle read in a reduce task (Figure \ref{fig:reducetask}). 
In addition, the heuristic algorithm can achieve a balanced pre-scheduling result, thus providing ~$80\%$ improvement in reduce stage completion time (Figure \ref{fig:reducestage}).

In overall, SCache can help Spark decrease by ~$89\%$ overhead of the whole shuffle process.

\subsection{Terasort}
We also evaluate Terasort\footnote{https://github.com/ehiggs/spark-terasort}-a recognized shuffle intensive benchmark for distributed system analysis.
Terasort consists of two consecutive shuffles. 
The first shuffle reads the input data and uses a hash partition function for re-partitioning. 
As shown in Figure \ref{fig:terasort}, Spark with SCache runs 2 $\times$ faster during the reduce stage of the first shuffle, which is consistent with the results in Section \ref{simpledag}. 
It further proves the effectiveness of SCache's optimization.

The second shuffle of Terasort partitions the data through a Spark RangePartitioner. 
% As the range bounds set by range partitioner almost match the same pattern of the first shuffle, almost $93\%$ of input data is from one particular map task for each reduce task. So we take the second shuffle as an extreme case to evaluate the scheduling locality for SCache.
In the second shuffle, almost $93\%$ of input data of a reduce task is produced by one particular map task. 
So we take the second shuffle as an extreme case to evaluate the heuristic locality swap of SCache.
In this shuffle, Spark schedules a reduce task to the node that produces most input data. 
By doing this, Spark minimizes the shuffle data through network. 
At the same time, Figure \ref{fig:terashuffle} reveals that SCache produces exactly same network traffic as Spark. 
It implies that the heuristic locality swap of SCache can obtain the best locality while balancing the load.

@@

\subsection{Production Workload}
We also evaluate some queries from TPC-DS\footnote{http://www.tpc.org/tpcds/}. 
TPC-DS benchmark is designed for modeling multiple users submitting varied queries (e.g. ad-hoc, interactive OLAP, data mining, etc.). 
TPC-DS contains 99 queries and is considered as the standardized industry benchmark for testing big data systems. 
% We evaluate the performance of Spark with SCache by picking some of the TPC-DS queries with shuffle intensive attribute. 
As shown in Figure \ref{fig:tpcds}, the horizontal axis is query name and the vertical axis is query completion time. 
Note that we skip some queries due to the compatible issues. 
Spark with SCache outperforms the original Spark in almost all tested queries. 
Furthermore, in many queries, Spark with SCache outperforms original Spark by an order of magnitude. 
It is because that those queries contain shuffle-heavy operations such as "groupby", "union", etc.
The overall reduction portion of query time that SCache achieved is 40\% on average. 
Since this evaluation presents the overall job completion time of queries, we believe that our shuffle optimization is promising.
% \begin{figure}
% 	\begin{subfigure}{\linewidth}
% 		\centering
% 		\includegraphics[width=0.6\linewidth]{fig/tera}
% 		\caption{Reduce Stage Completion Time Comparison of First Shuffle}
% 		\label{fig:terasort}
% 	\end{subfigure}
% 	\vspace{0.08cm}
% 	\begin{subfigure}{\linewidth}
% 		\centering
% 		\includegraphics[width=0.6\linewidth]{fig/tera_shuffle}
% 		\caption{Shuffle Data through Network Comparison of Second Shuffle}
% 		\label{fig:terashuffle}
% 	\end{subfigure}
% 	\caption{Terasort Evaluation}
% \end{figure}
\subsection{Overhead of Sampling}
We evaluate the overhead of sampling with different input sizes and numbers of nodes. 
In Figure \ref{fig:sampling}, the overhead of sampling only grows with the increase of input size on each node, but remains relatively stable when the cluster size scales up.
Since the shuffle data is short-lived, write-once, and read-once, the central controller of SCache does not have to collect and manage complex metadata. 
Meanwhile, most of the optimizations such as fetching and storing shuffle data are finished by workers independently. 
So the cost of pre-scheduling algorithm and memory management are unlikely to make the master become the bottleneck of the scalability.
Combined with the sampling overhead evaluation, we believe that SCache is scalable.
